\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-09 doc/paper.tex
doc/paper.tex: conform to -ize convention
doc/paper.tex: match firstly ... secondly ...

\section{Program Summary}
\noindent{\em Program title:} \fs\\ {\em Program obtainable from:}
         {\tt http://flexiblesusy.hepforge.org/}\\ {\em Distribution
           format:}\/ tar.gz\\ {\em Programming language:} {\tt
           C++, Wolfram/\mathematica, FORTRAN, Bourne shell}\\ {\em Computer:}\/ Personal computer\\ {\em Operating
           system:}\/ Tested on Linux 3.x, Mac OS X\\
         {\em External routines:}\/ SARAH 4.0.4, Boost library,
         Eigen, LAPACK\\ {\em
           Typical running time:}\/ 0.06-0.2 seconds per parameter
         point.\\ {\em Nature of problem:}\/ Determining the mass
         spectrum and mixings for any supersymmetric model. The
         generated code must find simultaneous solutions to
         constraints which are specified at two or more different
         renormalization scales, which are connected by
         renormalization group equations forming a large set of
         coupled first-order differential equations. \\ {\em Solution method:}\/
         Nested iterative algorithm and numerical minimisation of the
         Higgs potential.  \\ {\em Restrictions:} The couplings must
         remain perturbative at all scales between the highest and
         lowest boundary condition.  \fs~ assumes that all couplings
         of the model are real (i.e.\ $CP-$conserving). Due to the
         modular nature of the generated code adaption and extension
         to overcome restrictions in scope is quite straightforward.

@@

Recent experimental developments have also increased the relevancy of
such a tool. From the recent $7$ TeV and $8$ TeV runs at the Large
Hadron Collider (LHC) there have been two important developments.
First low energy signatures expected from such models, such as the
classic jets plus missing transverse energy signature, have not been
observed, substantially raising the lower limit on sparticle masses
(see e.g.~\cite{Aad:2013wta,Chatrchyan:2014lfa}). No other signature
of beyond the standard model (BSM) physics has been observed, leaving
the fundamental questions which motivated BSM physics
unanswered. Secondly ATLAS and CMS discovered \cite{ATLAS:2012ae,
  Chatrchyan:2012tx} a light Higgs of $125$ GeV, within the mass range
that could be accommodated in the MSSM but requiring stops which are
significantly heavier than both the direct collider limits and
indirect limits that appears in constrained models from the
significantly higher limits on first and second generation squarks.

>>>>

\section{Program Summary}
\noindent{\em Program title:} \fs\\ {\em Program obtainable from:}
         {\tt http://flexiblesusy.hepforge.org/}\\ {\em Distribution
           format:}\/ tar.gz\\ {\em Programming language:} {\tt
           C++, Wolfram/\mathematica, FORTRAN, Bourne shell}\\ {\em Computer:}\/ Personal computer\\ {\em Operating
           system:}\/ Tested on Linux 3.x, Mac OS X\\
         {\em External routines:}\/ SARAH 4.0.4, Boost library,
         Eigen, LAPACK\\ {\em
           Typical running time:}\/ 0.06-0.2 seconds per parameter
         point.\\ {\em Nature of problem:}\/ Determining the mass
         spectrum and mixings for any supersymmetric model. The
         generated code must find simultaneous solutions to
         constraints which are specified at two or more different
         renormalization scales, which are connected by
         renormalization group equations forming a large set of
         coupled first-order differential equations. \\ {\em Solution method:}\/
         Nested iterative algorithm and numerical minimization of the
         Higgs potential.  \\ {\em Restrictions:} The couplings must
         remain perturbative at all scales between the highest and
         lowest boundary condition.  \fs~ assumes that all couplings
         of the model are real (i.e.\ $CP-$conserving). Due to the
         modular nature of the generated code adaption and extension
         to overcome restrictions in scope is quite straightforward.

@@

Recent experimental developments have also increased the relevancy of
such a tool. From the recent $7$ TeV and $8$ TeV runs at the Large
Hadron Collider (LHC) there have been two important developments.
Firstly low energy signatures expected from such models, such as the
classic jets plus missing transverse energy signature, have not been
observed, substantially raising the lower limit on sparticle masses
(see e.g.~\cite{Aad:2013wta,Chatrchyan:2014lfa}). No other signature
of beyond the standard model (BSM) physics has been observed, leaving
the fundamental questions which motivated BSM physics
unanswered. Secondly ATLAS and CMS discovered \cite{ATLAS:2012ae,
  Chatrchyan:2012tx} a light Higgs of $125$ GeV, within the mass range
that could be accommodated in the MSSM but requiring stops which are
significantly heavier than both the direct collider limits and
indirect limits that appears in constrained models from the
significantly higher limits on first and second generation squarks.
